upwell_IDX

### 2019-08-09 upwell_IDX.Rmd
UI

```{r}
library(tidyverse)
library(ggplot2)
library(circular)
```

@@

# Determining the upwelling indeces

@@

wind_UI <- wind_daily %>% 
  group_by(sites) %>% 
  mutate(ui.saws = mean_speed * (cos(dir_circ - 160))) %>% # Angle?
  drop_na

index <- wind_UI %>% 
  group_by(sites) %>% 
  select("date", "ui.saws") %>% 
  mutate(saws.condition = ifelse(ui.saws > 0, "upwelling", "downwelling"))

>>>>

```{r}
library(tidyverse)
library(ggplot2)
library(circular)
# devtools::install_github("robwschlegel/coastR")
library(coastR)
library(gridExtra)
library(dplyr)
library(geosphere)
```

@@

# Determining the angle perpendicular to the coastline and plotting it

```{r}
south_africa_away_wide <- transects(site_list_sub, spread = 30)

world_map <- ggplot() + 
  borders(fill = "grey40", colour = "black")

# Create titles
titles <- c("Shore-normal", "Islands")

# Plotting function
plot_sites <- function(site_list, buffer, title_choice, dist){

  # Find the point 200 km from the site manually to pass to ggplot
  heading2 <- data.frame(geosphere::destPoint(p = select(site_list, lon, lat),  
                                              b = site_list$heading, d = dist))

  # Add the new coordinates tot he site list
  site_list <- site_list %>% 
    mutate(lon_dest = heading2$lon,
           lat_dest = heading2$lat)

  # Visualise
  world_map +
    geom_segment(data = site_list, colour = "red4", 
                 aes(x = lon, y = lat, xend = lon_dest, yend = lat_dest)) +
    geom_point(data = site_list, size = 3, colour = "black", aes(x = lon, y = lat)) +
    geom_point(data = site_list, size = 3, colour = "red", aes(x = lon_dest, y = lat_dest)) +
    coord_cartesian(xlim = c(min(site_list$lon - buffer), 
                             max(site_list$lon + buffer)),
                    ylim = c(min(site_list$lat - buffer), 
                             max(site_list$lat + buffer))) +
    labs(x = "", y = "", colour = "Site\norder") +
    ggtitle(titles[title_choice])
}

south_africa_away <- plot_sites(south_africa_away_wide, 1, 1, 100000)
```

# Determining the upwelling indeces by changing the angle for each of the sites

@@

wind_angle <- wind_daily %>% 
  dplyr::rename(site = sites) %>% 
  left_join(south_africa_away_wide[,c(2,21)], by = "site") %>% 
  dplyr::rename(coast_angle = heading)

##### Do this
wind_UI <- wind_daily %>% 
  mutate(ui.saws = mean_speed * (cos(dir_circ - coast_angle))) %>% 
  drop_na

index <- wind_UI %>% 
  group_by(sites) %>% 
  select("date", "ui.saws") %>% 
  mutate(saws.condition = ifelse(ui.saws < 12.5, "upwelling"))
